Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2011-02-17 results.tex
Length scale study beginning...

>>>>

\subsection{Length scale study}

Debye's length $\lambda_D$ is commonly used to estimate the screening length in electrolyte
solutions. In the given PNP model, it serves as well as an estimation of the boundary layer thickness
--- thickness of the layer in the vicinity of the boundaries $\partial\Omega_1$ 
and $\partial\Omega_2$  where $c \neq 1$.
The Debye's length in all the previous simulations was determined by the constants in
Table~\ref{Table:used-constants}: $\lambda_D=XXX$. It is known that computation gets increasingly
difficult with reducing the value of $\lambda_D$.
It was our interest to see how small length scales can Hermes HP\_ANISO automatic
adaptivity handle. The parameter $\varepsilon$ was varied as follows:
$$\varepsilon_n=\varepsilon\times 0.5^n$ where $\varepsilon$ is taken from Table~\ref{Table:used-constants}.
